---
title: "INITIALIZATION WORKFLOW"
output: html_document
date: '2022-11-28'
---

This process uses `df` generated from `global.R`, so it won't work on knit

Parse HTML from Original (OG) Bank of Card's that Stewart learned to get cards
for Emma to learn

Output to Excel `OG Bank Parsed_raw.csv`
which should be manually combed through to check the parsing

When the check is done save as `OG Bank Parsed.xlsx`

```{r parse og bank, warning=FALSE}
library(readr)
library(tidyr)
library(stringr)
library(dplyr)
library(tidyverse)

regex_for_japanese<-"[\\x{3041}-\\x{3096}\\x{30A0}-\\x{30FF}\\x{3400}-\\x{4DB5}\\x{4E00}-\\x{9FCB}\\x{F900}-\\x{FA6A}\\x{2E80}-\\x{2FD5}\\x{FF5F}-\\x{FF9F}\\x{3000}-\\x{303F}\\x{31F0}-\\x{31FF}\\x{3220}-\\x{3243}\\x{3280}-\\x{337F}]"

# Prep original dataframe
df.group0 <- df %>%
  filter(deck == 'OG Bank') %>%
  select(fields) %>%
  rowid_to_column("index")
  
# Group 1 = Ends With Japanese and then the word
df.group1 <- df.group0 %>%
  mutate(MyWord = sub(".*\\]", "", fields)) %>%
  mutate(MyWord = sapply(str_extract_all(MyWord, regex_for_japanese),
                         function(x) paste(x,collapse=""))) %>%
  filter(nchar(MyWord) != 0)
  
# Group 2 = Starts With <div>
df.group2 <- df.group0 %>%
  anti_join(df.group1, by = 'index') %>%
  mutate(first_4_characters = substr(fields, 1, 4)) %>%
  filter(first_4_characters == "<div") %>%
  separate(col = 'fields', into = c('first_div_contents',NA), sep = "</div>", remove = FALSE) %>%
  mutate(MyWord = sub(".*\\]", "", first_div_contents)) %>%
  mutate(MyWord = sapply(str_extract_all(MyWord, regex_for_japanese),
                         function(x) paste(x,collapse=""))) %>%
  select(-first_4_characters, -first_div_contents) %>%
  arrange(fields)

# Group 3 = Starts With Japanese
df.group3 <- df.group0 %>%
  anti_join(df.group1, by = 'index') %>%
  anti_join(df.group2, by = 'index') %>%
  separate(col = 'fields', into = c('MyWord',NA), sep = "<", remove = FALSE) %>%
  separate(col = 'MyWord', into = c('MyWord',NA), sep = "&", remove = TRUE) %>%
  separate(col = 'MyWord', into = c('MyWord',NA), sep = " ", remove = TRUE) %>%
  arrange(MyWord)

df_out <- rbind(df.group1,df.group2,df.group3) %>%
  select(MyWord, fields)

write_excel_csv(df_out, file = 'OG Bank Parsed_raw.csv')

```

Generate Initial To-Learn List

This uses the combed through Excel `OG Bank Parsed.xlsx`

- Combine two sources of words to list
  - OG Bank (Words that Stewart learned)
  - Core 10K (Static Frequency List from the internet)
- Create ranking based on order in each of the two sources `rank.order`
- Initialize other two columns used in active version of Learning List
  - `rank.never_learn` 
  - `rank.delay_bonus`

The To-Learn List is saved as RDS in this folder `df.to_learn.RDS`

If you want to use this one in the app, it should be moved to
the `/global` folder

```{r generate initial learning list}
library(readxl)
library(readr)

df.bank <- read_excel("OG Bank Parsed.xlsx")
df.Core_10K <- read_excel("Core_10K.xlsx")

# Add index to bank
df.bank <- df.bank %>%
  rowid_to_column("index")

# Rank index on bank and core 10k by 1000's, drop un-needed columns
df.bank <- df.bank %>%
  mutate(rank.order_bank = round(index, -3)) %>%
  select(-index)
df.Core_10K <- df.Core_10K %>%
  mutate(rank.order_core10k = round(index, -3)) %>%
  select(MyWord, rank.order_core10k)

# Full Join Banks to get all potential words to learn
## Anti join already learned words
df.to_learn <- full_join(df.bank,
          df.Core_10K, 
          by = "MyWord")

# Combine Rank Orders for bank and core 10k into a single metric
## Words that are unique to one source are given an equal rank in the source
## that does not contain that word
df.to_learn <- df.to_learn %>%
  mutate(rank.order_bank = if_else(is.na(rank.order_bank)== TRUE, 
                                   rank.order_core10k, rank.order_bank)) %>%
  mutate(rank.order_core10k = if_else(is.na(rank.order_core10k)== TRUE, 
                                      rank.order_bank, rank.order_core10k)) %>%
  mutate(rank.order = rank.order_bank + rank.order_core10k) %>%
  select(-rank.order_bank, -rank.order_core10k)

# Add additional columns that are populated through app, and sort
df.to_learn <- df.to_learn %>%
  mutate(rank.never_learn = 0) %>%
  mutate(rank.delay_bonus = 0) %>%
  mutate(rank.unseen_kanji = 0) %>%
  mutate(rank.already_learned = 0) %>%
  arrange(rank.never_learn,
          rank.already_learned,
          rank.unseen_kanji,
          rank.order + rank.delay_bonus)

# Save as RDS
saveRDS(df.to_learn, file="List - To Learn.RDS")
```
